\subsection{Armour}

\begin{longtable}{|C{2cm} L{2cm} L{2cm} L{8cm}|}
\hline
\large{\textbf{Name}} &
\large{\textbf{Cost}} &
\large{\textbf{Slot}} &
\large{\textbf{Resistance}}
\\ \hline
\WeaponRow{Gambeson}{100 m}{4}{
\textbf{Whole body, except head:} \hfill \break
\textit{Slashing:} $+15\%$ \hfill \break
\textit{Crushing:} $+15\%$ \hfill \break
\textit{Piercing:} $+15\%$ \hfill \break
\textit{Cold:} $+20\%$ \hfill \break
\textit{Hot:} $-20\%$
}{A \textbf{gambeson} or \textbf{aketon} is basically \SoCalled{cloth armour}, as it is made out of various textiles and fabrics, typically linen or wool, stuffed to increase damage absorption. Because a gambeson is effectively a padded jacket, it also provides defence against the cold - effectively doubling as a winter coat -, though it also accelerates overheating in particularly hot conditions. Gambesons can be worn on their own, but they are also worn under other types of armour - in fact, a gambeson is mandatory to be born under any heavier armour.}
\WeaponRow{Leather Armour}{80 m}{5}{
\textbf{Whole body, except head:} \hfill \break
\textit{Slashing:} $+10\%$ \hfill \break
\textit{Crushing:} $+10\%$ \hfill \break
\textit{Piercing:} $+10\%$
}{\textbf{Leather Armour} is made out of boiled and hardened leather. It is a rather lightweight piece of armour that preserves the user's mobility at the expense of providing only minimal amount of extra protection. \textbf{Just like every other piece of armour that isn't gambeson, Leather Armour is always worn over a gambeson, never on its own.}}
\WeaponRow{Chainmail}{200 m}{5}{
\textbf{Whole body, except head:} \hfill \break
\textit{Slashing:} $+100\% \pm modifiers$ \hfill \break
\textit{Crushing:} $+5\% \pm modifiers$ \hfill \break
\textit{Piercing:} $+5\% \pm modifiers$
}{\textbf{Chainmail} is a type of armour made by linking metal rings together to form a mesh - such armour provides complete immunity to slashing damage when in pristine condition, but can't do much against piercing and crushing damage. \textbf{Just like every other piece of armour that isn't gambeson, Chainmail is always worn over a gambeson, never on its own.}}
\WeaponRow{Scalemail}{220 m}{5}{
\textbf{Whole body, except head:} \hfill \break
\textit{Slashing:} $+100\% \pm modifiers$ \hfill \break
\textit{Crushing:} $+20\% \pm modifiers$
}{\textbf{Scalemail} - also known as \textbf{Lamellar Armour} -, is a type of body armour, made from small rectangular plates \textit{(scales or \textbf{lamellae})} of any tpye of metal, leather \textit{(rawhide)}, or bones laced into horizontal rows. Lamellar Armour offers better protection against blunt force trauma than Chainmail, but the gaps between the lamellae negate the protection against piercing damage. \textbf{Just like every other piece of armour that isn't gambeson, Scalemail is always worn over a gambeson, never on its own.}}
\WeaponRow{Breastplate}{220 m}{6}{
\textbf{Torso:} \hfill \break
\textit{Slashing:} $+100\% \pm modifiers$ \hfill \break
\textit{Piercing:} $+30\% \pm modifiers$ \hfill \break
\textit{Crushing:} $+30\% \pm modifiers$
}{\textbf{Breastplate} is a type of armour made from multiple joined solid pieces - plates - that wrap around the wearer's chest, usually made out of metal. It offers protection against slashing, piercing and crushing damage alike. \textbf{Just like every other piece of armour that isn't gambeson, Breastplate is always worn over a gambeson, never on its own - because it occupies the 6th slot, it can also be worn over a Chainmail, Scalemail or Leather Armour as well.}}
\WeaponRow{Brigandine}{200 m}{6}{
\textbf{Torso:} \hfill \break
\textit{Slashing:} $+100\% \pm modifiers$ \hfill \break
\textit{Piercing:} $+20\% \pm modifiers$ \hfill \break
\textit{Crushing:} $+20\% \pm modifiers$
}{A \textbf{Brigandine} is an alternative type of Breastplate, made with riveting metal plates to heavy cloth - as a result, it provides lesser amount of protection, but is lighter and offers more flexibility. \textbf{Just like every other piece of armour that isn't gambeson, Brigandine is always worn over a gambeson, never on its own - because it occupies the 6th slot, it can also be worn over a Chainmail, Scalemail or Leather Armour as well.}}
\WeaponRow{Platemail}{500 m}{5 and 6}{
\textbf{Whole body, except head:} \hfill \break
\textit{Slashing:} $+100\% \pm modifiers$ \hfill \break
\textit{Piercing:} $+30\% \pm modifiers$ \hfill \break
\textit{Crushing:} $+30\% \pm modifiers$
}{\textbf{Platemail} takes the same concept as the Breasatplate, but expands it to the whole body, save for the head. \textbf{Just like every other piece of armour that isn't gambeson, Platemail is always worn over a gambeson, never on its own.}}
\end{longtable}
