\subsection{Helmets}

\begin{longtable}{|C{2cm} L{2cm} L{2cm} L{8cm}|}
\hline
\large{\textbf{Name}} &
\large{\textbf{Cost}} &
\large{\textbf{Slot}} &
\large{\textbf{Resistance}}
\\ \hline
\WeaponRow{Padded Coif}{75 m}{1}{
\textbf{Head:} \hfill \break
\textit{Slashing:} $+15\%$ \hfill \break
\textit{Crushing:} $+15\%$ \hfill \break
\textit{Piercing:} $+15\%$ \hfill \break
\textit{Cold:} $+20\%$ \hfill \break
\textit{Hot:} $-20\%$
}{A \textbf{Padded Coif} is made out of padded textiles that wrap around the wearer's head - it is basically a Gambeson for the Head, although it only protects the top, the back and the sides of the head, not the front.}
\WeaponRow{Chainmail Coif}{100 m}{2}{
\textbf{Head:} \hfill \break
\textit{Slashing:} $+50\% \pm modifiers$ \hfill \break
\textit{Crushing:} $+5\% \pm modifiers$ \hfill \break
\textit{Piercing:} $+5\% \pm modifiers$
}{A \textbf{Chainmail Coif} is made by linking metal rings together, just like a Chainmail Hauberk - as the name suggests, it is Chainmail for the Head. \textbf{A Chainmail Coif cannot be worn on its own, and must be worn over a Padded Coif}.}
\WeaponRow{Nasal Helmet}{100 m}{32}{
\textbf{Head:} \hfill \break
\textit{Slashing:} $+75\% \pm modifiers$ \hfill \break
\textit{Crushing:} $+15\% \pm modifiers$ \hfill \break
\textit{Piercing:} $+10\% \pm modifiers$
}{A \textbf{Nasal Helmet} is a metal helmet protecting the top of the head, and hhe centre of the front by projecting a bar that covers the nose. While not mandatory, it is highly recommended to be born over a Chainmail Coif.}
\WeaponRow{Kettle Helmet}{100 m}{3}{
\textbf{Head:} \hfill \break
\textit{Slashing:} $+55\% \pm modifiers$ \hfill \break
\textit{Crushing:} $+35\% \pm modifiers$ \hfill \break
\textit{Piercing:} $+5\% \pm modifiers$
}{A \textbf{Kettle Helmet} is a metal helmet made in the shape of a brimmed hat - it protects against blows that come from the top, and is thus typically worn by warriors who expect to be struct from above by a horseman, such as archers and crossbowmen. Just like the Nasal Helmet, it is not mandatory, but highly recommended to wear a Chainmail Coif underneath the Kettle Helmet.}
\WeaponRow{Great Helm}{150 m}{3}{
\textbf{Head:} \hfill \break
\textit{Slashing:} $+100\% \pm modifiers$ \hfill \break
\textit{Crushing:} $+30\% \pm modifiers$ \hfill \break
\textit{Piercing:} $+30\% \pm modifiers$ \hfill \break
\textit{Hot:} $-30\%$
}{The \textbf{Great Helm} is an evolution of the Nasal Helmet, having evolved by gradually adding more and more parts to it, until the end result was a flat-topped cylinder that completely covers the head and only has very small openings for ventilation and vision. While offering a great deal of protection, the obstruction of vision and hearing gives the wearer a \Malus{1} to Dexterity while wearing it, and the limited space for ventilation heavily accelerates the user overheating in hot conditions.}
\WeaponRow{Bascinet \& Visor}{175 m}{3}{
\textbf{Head:} \hfill \break
\textit{Slashing:} $+100\% \pm modifiers$ \hfill \break
\textit{Crushing:} $+30\% \pm modifiers$ \hfill \break
\textit{Piercing:} $+30\% \pm modifiers$ \hfill \break
\textit{Hot:} $-20\%$
}{The \textbf{Bascinet \& Visor} is an evolution of the Great Helm, effectively splitting the helmet into two parts: the Bascinet that covers the top, back and sides of the head, and the Visor, which protects the front of the face, and can be lifted up any time to reveal the identity of the wearer, or to make breathing easier. Bascinets offer the same amount of protection that Great Helms do, but without the Dexterity malus \textit{(and a reduced malus to Heat resistance)}, due to the rounded visors offering greater amount of vision and better ventilation.}
\WeaponRow{Barbute}{150 m}{3}{
\textbf{Head:} \hfill \break
\textit{Slashing:} $+90\% \pm modifiers$ \hfill \break
\textit{Crushing:} $+20\% \pm modifiers$ \hfill \break
\textit{Piercing:} $+10\% \pm modifiers$ \hfill \break
}{The \textbf{Barbute} can be most easily described as a Visorless Bascinet, but modified maximize the protection the wearer receives without a visor, while still maintaining great vision. The lack of visor also ensures much better ventilation than the bascinet.}
\end{longtable}
