\section{Items, Equipment and Inventory}
Each character has an \textbf{equipment} and an \textbf{inventory}. The earlier is the a map of equipment slots and \textbf{items} equipped on those respective slots, while the latter is a list of items that the character is currently carrying, but not wearing or using.\newline
Items include weapons, clothing, armour, currency, food, beverages, potions, keys, books, scrolls, and various other articles of tangible personal property. A character's weight-carrying capacity depends on their endurance, while their maximal inventory capacity depends on equipped items, such as backpacks and bags. Equipment slots include:
\begin{itemize}
\item \textbf{Hands:} Most races have two, though some may have more, or none at all. Some negative status effects may also reduce their numbers for each characters, like for a human whose left hand was cut off. Weapons and shields occupy hands. Some weapons \textemdash the majority of ranged weapons for example \textemdash may occupy two hands at once. The hands may be occupied by various other items too, such as instruments of work or music.
\item \textbf{Fingers:} Their number depends on the number of hands, and the race's number of fingers per hand, with most races having five fingers per hand. Potentially occupied by rings. All fingers belonging to a hand may also be occupied by gloves or gauntlet.
\item \textbf{Head:} Occupied by potentially multiple stacking layers of headwear \textit{(for example, a gambeson cap, combined with a chainmail coif, and finally a bascinet)}.
\item \textbf{Face:} Occupied by potentially multiple stacking layers of jewelry that can cover the face, the ears, mouth, etc.
\item \textbf{Torso:} Occupied by potentially multiple stacking layers of clothing or armour \textit{(for example, an undershirt at the bottom, followed by a gambeson, then chainmail, and finally a breastplate)}.
\item \textbf{Shoulders:} Potentially occupied by pauldrons.
\item \textbf{Arms:} Potentially occupied by jewelry \textit{(such as torcs)} or protective armbands.
\item \textbf{Neck:} Potentially occupied by jewelry \textit{(such as necklaces or torcs)}.
\item \textbf{Legs:} Occupied by potentially multiple stacking layers of clothing or armour \textit{(for example, a loincloth at the bottom, followed by a pants, then chainmail and some leg-protecting plates)}.
\item \textbf{Feet:} Occupied by potentially multiple stacking layers of clothing or armour \textit{(for example, socks followed by boots)}.
\item \textbf{Back:} Capes or backpacks. The earlier are purely aesthetic \textit{(and can potentially impede movement)}, while the latter increase carryweight/inventory capacity.
\end{itemize}
