\subsection{Striking Weapons}

\begin{longtable}{|C{2cm} L{2cm} L{2cm} L{8cm}|}
\hline
\large{\textbf{Name}} &
\large{\textbf{Cost}} &
\large{\textbf{Handedness}} &
\large{\textbf{Damage}}
\\ \hline
\WeaponRow{Club}{65 m}{One}{
\textit{Crushing:} $\frac{2d8 \pm modifiers}{5}*Strength$
}{Clubs are the most primitive and crude of all weapons, typically improvised rather than manufactured on purpose, they are literally nothing more than blunt sticks, often with one end thicker than the other, used to inflict blunt-force trauma on one's opponents. Not much else can be said about them.}
\WeaponRow{Mace}{85 m}{One}{
\textit{Crushing:} $\frac{2d10 \pm modifiers}{5}*Strength$
}{More technologically advanced than clubs, maces expand upon the same concept - causing blunt force trauma - and improve upon it by concentrating said blunt force to a smaller area, where the weapon's weight is concentrated.}
\WeaponRow{Morning Star}{95 m}{One}{
\textit{Crushing:} $\frac{2d10 \pm modifiers}{5}*Strength$ \hfill \break
\textit{Piercing:} $\frac{1d4 \pm modifiers}{5}*Strength$
}{Spiked Maces. The spikes cause extra piercing damage to the enemies, and are good for penetrating armour - otherwise, they function identically to regular maces.}
\WeaponRow{Flail}{115 m}{One}{
\textit{Crushing:} $\frac{2d12 \pm modifiers}{5}*Strength$ \hfill \break
\textit{Piercing:} $\frac{1d4 \pm modifiers}{5}*Strength$
}{A Flail is a variant of the Mace or Morning Star, with one key difference the \textit{(spiked)} ball isn't attached directly to the weapon's handle, but is rather attached via a chain or rope. This allows the weapon's user to build up momentum during a strike more effectively, but also comes at the expense of accuracy.}
\WeaponRow{Warhammer}{95 m}{Two}{
\textbf{Blunt face:} \hfill \break
\textit{Crushing:} $\frac{2d12 \pm modifiers}{5}*Strength$ \hfill \break
\textbf{Pointy beak:} \hfill \break
\textit{Piercing:} $\frac{2d6 \pm modifiers}{5}*Strength$ \hfill \break
\textit{Crushing:} $\frac{2d6 \pm modifiers}{5}*Strength$
}{A warhammer is an adaptation of the hammer used in blacksmithing for military purposes, expanded into a two-handed weapon. Warhammers typically have a flat face for pure blunt force trauma, and a pointy beak for inflicting piercing damage, usually for penetrating armour.}
\WeaponRow{Axe}{80 m}{One / Two}{
\textit{Slashing:} $\frac{2d6 \pm modifiers}{5}*Strength$ \hfill \break
\textit{Crushing:} $\frac{2d6 \pm modifiers}{5}*Strength$
}{An axe is effectively a wedge attached to a handle, commonly used both as a weapon and a tool. The wedge is typically sharpened to a degree, which means that axes simultaneously cause slashing and crushing damage.}
\WeaponRow{Bearded Axe}{100 m}{Two}{
\textit{Slashing:} $\frac{2d8 \pm modifiers}{5}*Strength$ \hfill \break
\textit{Crushing:} $\frac{2d8 \pm modifiers}{5}*Strength$
}{A variation of the axe further specialized for combat usage, a bearded axe has a larger blade and a longer handle than its humbler counterpart.}
\end{longtable}
