\section{Attributes and Vitals}
Each and every character has a number of assigned variables we call \textbf{attributes and vitals}. \textbf{Attributes} are, for the most part fixed for a character \textit{(though some events can alter them)}, but very often modified by status effects \textemdash they tend to range between 0 and 20 for playable characters, with 10 being an average value. \textbf{Vitals} on the other hand are constantly changing, and are measured against certain set maximums and minimums.\newline
\textbf{Attributes} include:
\begin{itemize}
\item \textbf{Strength:} Governs the damage of bow-type ranged weapons \textit{(strength below a certain number of certain bows results in range penalty or inability to even use the bow)} and the damage of blunt weapons. Strength also governs the efficency of unarmed combat. Outside of a combat context, strength will also govern the character's ability to lift heavy objects, affencting carrying capacity among other things. Having high strength comes with the drawback of increasing a character's need for protein, unless the character is undead.
\item \textbf{Endurance:} Governs the maximum number of hitpoints per body part, as well as the character's maximum stamina. High endurance also increases a character's resistance to diseases and poisons. Having high endurance comes with the drawback of increasing a character's need for fat, unless the character is undead.
\item \textbf{Dexterity:} Governs damage of piercing weapons like spears and bladed weapons such as swords, accuracy of ranged weapons, evasion chance, stealth, lockpicking, etc. Having high dexterity comes with the drawback of increasing a character's need for protein, unless the character is undead.
\item \textbf{Intelligence:} Governs the character's maximum \textit{mana/spellpoints} count, if the character is using Arcane Magic. Whether the character is a spellcaster or not, intelligence also governs a character's experience gain \textit{(the higher the intelligence, the faster the level-ups)}, aids the character at detecting things that seem unusual. Having high intelligence also comes with the drawback of increasing a character's need for carbohydrates, unless the character is undead.
\item \textbf{Willpower:} Governs magic resistance for all character, as well as the maximum \textit{mana/spellpoints} for characters that use Clerical Magic. While it increases the character's magic resistance as a whole, it especially increases resistance to mind control. NPCs with high willpower also tend to be resistant to bribery and seduction attempts. Unlike strength, endurance or dexterity, willpower does not come with the drawback of increasing the character's nutritional needs.
\item \textbf{Charisma:} Governs a character's ability to lead, convince, explain, seduce, and various other social interactions. Highly charismatic characters can talk monsters to death, while characters with low charisma will be forced to rely on favors, money or brute strength to get what they want. For characters that use Arcane Magic, Charisma governs their ability to use spells that contradict their alignment, such as Good characters using Dark Magic and Evil characters using Light Magic, with Arcane Magic users that have high Charisma having no penalties from using opposite-alignment spells. Unlike strength, endurance or dexterity, charisma does not come with the drawback of increasing the character's nutritional needs, but a disproportionate number of negative status effects reduce charisma.
\end{itemize}
\textbf{Vitals} include:
\begin{itemize}
\item \textbf{Hitpoints:} Represents how much damage the character can still sustain, unlike all the other vitals, hitpoints are counted separately for each body part of the character. Reaching zero hitpoints on vital body parts means death.
\item \textbf{Mana:} Relevant only to spellcasting character, it determines how much magical power they have left and can use to cast spells. Running out of mana means not being able to cast spells until they recover their mana via either resting or drinking mana potions.
\item \textbf{Protein:} The amount of protein in the character's system, expressed in grams. The character's need for protein is governed by their race, sex, strength and dexterity. Having under 50\% of their protein need causes the character's strength and dexterity to degrade linearly. \textbf{This vital is inactive for undead characters.}
\item \textbf{Carbohydrate:} The amount of carbohydrates in the character's system, expressed in grams. The character's need for carbohydrates is governed by their race, sex and intelligence. Having under 50\% of their carbohydrate need causes the character's intelligence to degrade linearly. \textbf{This vital is inactive for undead characters.}
\item \textbf{Fat:} The amount of fat in the character's system, expressed in grams. The character's need for fat is governed by their race, sex and endurance. Having under 50\% of their fat need causes the character's endurance to degrade linearly. \textbf{This vital is inactive for undead characters.}
\item \textbf{Calories:} Total calories in the character's system. Effectively \[(other+(4*protein)+(4*carbohydrate)+(9*fat))\], since each gram of protein is 4 calories, each gram of carbohydrates is 4 calories, and each gram of fat is 9 calories. Other calories can include every other sources of calory, but among them is chiefly alcohol, with each gram of alcohol being 7 calories. \textbf{This vital is inactive for undead characters} \textemdash otherwise, a character that reaches zero calory count starves to death. Overeating has negative consequences, like temporarily reducing dexterity and charisma.
\item \textbf{Alcohol:} The amount of alcohol in the character's system, expressed in blood alcohol content \textit{(a percentage of ethanol in the blood in units of mass of alcohol per volume of blood)}, primarily to determine the character's level of intoxication. \textbf{This vital is inactive for undead characters} \textemdash otherwise, blood alcohol content above 0.500 is lethal \textit{(death by alcohol poisoning)}, blood alcohol content between 0.500 and 0.029 equates to varying levels of drunkenness, and blood alcohol content below 0.029 has no symptoms \textit{(the character is for all intents and purposes sober)}.
\item \textbf{Water:} The hydration level of your character \textemdash unlike other counters, it is more like a timer that gets reset to 3.0 when the character is hydrated. \textbf{This vital is inactive for undead characters} \textemdash otherwise characters die of dehydration when their water level reaches zero.
\item \textbf{Blood:} The amount of foreign blood in the character's system. For vampires and theriantropes, the need for blood replaces the need for nutrients like protein, carbohydrates, fat, calories and water \textemdash as such \textbf{this vital is only active for vampires and theriantropes.}
\item \textbf{Energy:} Effectively how un-sleepy the character is. This one is active even for undead characters, since all sentient beings need rest \textemdash if not physical, then mental. It slowly and gradually depletes over time \textit{(but depletes faster when the character is doing physically or mentally demanding work)}, and is regenerates very fast by sleeping \textit{(eight hours is enough to recover 100\% of a character's energy, no matter how depleted it was)} and also by consuming certain potions or beverages  \textit{(such as black tea)}. When it is depleted, the character spontaneously faints and falls asleep. When it is near depletion, the character is supposed to feel very drowsy and even experience episodes of microsleep and general confusion.
\end{itemize}
