\section{Body parts}
In the World of Artograch RPG, each and every \textbf{body part} has its own health meter. When that health meter is depleted, bad things can happen: if we're talking about a limb, the character is imparted with a negative status effect and certain equipment slots are bound to be disabled \textemdash if the body part in question is not a limb, then the depletion of its health points causes death \textit{(or unconsciousness, if house rules rule out death)}, as the vital body part in question is assumed to be destroyed.\newline
The exact number of body parts a character can have depends on their race, though most humanoid races have one head, one torso, two arms and two legs, out of which the head and the torso are vital, with depletion of its hitpoints causing death - while loss of arms and legs merely disables the corresponding inventory slots.\newline
The fact that each body part has its own health meter is one of the reasons why the World of Artograch roleplaying system is not recommended for actual tabletop roleplaying \textit{(in spite of technically being possible)}, but rather is intended to serve as the basis of computer-based adaptations.\newline
As most humanoid races have a single torso, a single head, two arms and two legs, below will be shown the health scaling for those body parts:\newline
\begin{tabular}{|c|c|c|c|c|c|}
\hline
\textbf{Torso} & \textbf{Head} & \textbf{Left Arm} & \textbf{Right Arm} & \textbf{Left Leg} & \textbf{Right Leg} \\ \hline
$\frac{\textit{Base HP\ast}}{1} $ & $ \frac{\textit{Base HP\ast}}{4} $ & $ \frac{\textit{Base HP\ast}}{5} $ & $ \frac{\textit{Base HP\ast}}{5} $ & $ \frac{\textit{Base HP\ast}}{2} $ & $ \frac{\textit{Base HP\ast}}{2} $ \\ \hline
\end{tabular}\newline
$ \textbf{\ast Base HP} $ is the character's $ \textbf{Endurance} \cdot 10 $, unless there are some other modifiers at play, such as status effects or feats. In other words, without any other modifiers, a typical humanoid character with an Endurance of 10 will have a torso with $ \frac{10 \cdot 10}{1} = 100 $ HP, a head with $ \frac{10 \cdot 10}{4} = 25 $ HP, a right arm and a left arm each with $ \frac{10 \cdot 10}{5} = 20 $ HP, and finally a right leg and a left lef each with $ \frac{10 \cdot 10}{2} = 50 $ HP.\newline
Chances to hit a certain body part also scale with the amount of maximum HP each body part can potentially have: if we add together 100, 25, 20, 20, 50 and 50, we get 265, which results in ratios of $ \frac{100}{265}=37.73\% $, $ \frac{25}{265}=9.43\% $, $ \frac{20}{265}=7.55\% $, $ \frac{20}{265}=7.55\% $, $ \frac{50}{265}=18.88\% $ and $ \frac{50}{265}=18.88\% $ respectively. But what does that exactly mean? It means that if the character simply attacks the enemy without targetting any particular body part, we generate a random number between 0 and 100, and then, if the number is is above 81, it is the right leg - if it's below that, but still above 62, it's the left leg, right arm if below that but above 55, left arm if below that but above 47, head if below that but above 38, and torso if below 38 - alternatively, in a more simplifeid dice-rolling system, one most use two 10-sided dice or four 5-sided dice, and the numbers are instead 16, 12, 11, 9, 8.\newline
If the attacker is attacking from a mount, the legs cannot be targeted and will never be hit, which means that the numbers should instead be $ \frac{100}{165}=60.60\% $, $ \frac{25}{165}=15.15\% $, $ \frac{20}{165}=12.12\% $, $ \frac{20}{165}=12.12\% $ - that is, above 88 for right hand, below that but above 76 for left hand, below that but above 61 for head, and below 61 for torso; with the numbers instead being 18, 15 and 12 for dice-rolling.
