\section{Melee Attack}
\textbf{Melee Attacks} are attacks done with a melee weapon up close. If both combatants are fighting with bladed weapons \textit{(swords)}, both combatants roll for a succesful hit and are trying to attack the same body part, and neither parties indicated any desire to prioritize defense over offense, they parry each other's attacks, leading to no damage - if one character decides to prioritize defense over offense, then any succesful roll for hitting will translate into parrying, no matter the targetted body part. It is impossible to parry with or against any melee weapon other than bladed weapons.
\subsection{Attack Types}
Melee Attacks can be neatly divided into four categories:
\begin{itemize}
  \item \textbf{Regular Attack:} A regular targeted or untargeted strike with your melee weapon. It has no drawbacks or advantages. All involuntary counterattacks are also regular attacks. All characters know how to do regular attacks by default too.
  \item \textbf{Power Attack:} An untargeted strike done with a greater swing, from a large distance, with a stronger momentum - this results in a stronger, but more inaccurate attacks, this means a \MalusPS{30\%} increase to chance of miss, but also a \Bonus{25\%} to all damage done in melee. By default, characters cannot do Power Attacks, and must unlock them via a feat - in the archmodule, that feat is Overswing.
  \item \textbf{Quick Attack:} Two untargeted strikes per at a turn, but each with an extra \MalusPS{30\%} increase to chance of miss, and also a \Malus{30\%} to all damage done in melee in case of landing a hit. By default, characters cannot do Quick Attacks, and must unlock them via a feat - in the archmodule, that feat is Flurry.
  \item \textbf{Mounted Attack:} A specialized untargeted strike from atop a mount \textit{(usually a horse)}, it requires the attacker to be moving while doing the attack \textit{(otherwise it's just a Regular Attack done from horseback)} - by default, this kind of attack comes with a \Bonus{40\%} at the cost of an extra \MalusPS{15\%} chance to miss the target. Just like Power Attack and Quick Attack, this needs to be unlocked via a feat - in the archmodule, that feat is Chevauchée.
\end{itemize}
\subsection{Unarmed Attacks}
When doing unarmed attacks, the damage done is $\frac{1d8}{4}*Strength$, unless some feats modify that. It is always \textbf{Crushing} type damage.
