\subsection{Armour}
Armour occupies various parts of the body, and can often be combined to constitute multiple stacking layers. The primary goal of armour is to provide resistance against attacks, primarily physical ones \textit{(tho enchanted armour may offer magic resistance)}. If we assume that a character's outfit - excluding jewellry - consists of a maximum of 6 \textit{slots/layers} \textit{(underwear, shirt, sweater, coat or gambeson, chainmail or leather armour, and finally a breastplate)}, then we can neatly divide types of armour into these main categories:
\begin{itemize}
\item \textbf{Gambeson:} Occupying the fourth outfit slot, it is effectively a padded jacket, it doubles as both a piece of armour and a winter coat, protecting its user from slashing damage and cold thermal damage. It doesn't offer much resistance against piercing and crushing damage. Gambeson is typically worn under other types of armour, thus combined with leather armour, chainmail, plate mail, etc.
\item \textbf{Leather Armour:} Occupying the fifth outfit slot, it is boiled and hardened leather processed into a piece of armour, it is typically worn over a gambeson, providing additional protection.
\item \textbf{Chainmail:} Occupying the fifth outfit slot, it is a series of metal chains linked together, it is pretty much always worn over a gambeson, augmenting it with resistance against slashing damage.
\item \textbf{Scalemail:} Occupying the fifth outfit slot, also known as \textbf{Lamellar Armour}, it is a type of body armour, made from small rectangular plates \textit{(scales or \textbf{lamellae})} of iron, leather \textit{(rawhide)}, or bronze laced into horizontal rows; it is pretty much always worn over a gambeson, augmenting it with resistance against slashing damage, and to a lesser extent, piercing damage.
\item \textbf{Breastplate:} Occupying the sixth outfit slot, it is typically multiple joined solid metal pieces - plates - that wrap around the wearer's chest, it offers protection against both slashing and piercing damage. It is typically worn over chainmail, or at the very least gambeson.
\item \textbf{Platemail:} Occupying both the fifth and sixth outfit slots, it is similar to a breastplate, but expanded to cover the whole body. A full suit of plate armour offers good protection against both piercing and crushing damage. It is always worn above a gambeson.
\end{itemize}
